Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
quotes

>>>>

\bigskip

\begin{flushright}{\slshape
    {Before I came across it, I had read many articles describing intricate properties of neurons, the many varieties of neurotransmitters and second-messenger molecules, synaptic modification processes, complex and hypercomplex cells, columns in the visual cortex, and so on.  All of this was fascinating but seemed very biological and microscopic:  altogether quite distant from everyday mental experiences.  I simply had never come across a cogent theory that addressed brain mechanisms on a global level.  Pentti Kanerva's memory model was a revelation for me: it was the very first piece of research I had ever come across that made me feel I could glimpse the distant goal of understanding how the brain works as a whole. It gave me a concrete sense for how familiar mental phenomena could be thought of as distributed patterns of micro-events, thanks to beautiful mathematics.
	.} \\ \medskip
    --- Douglas Hofstadter}
\end{flushright}
\bigskip
\bigskip
